Combinatorics of the geometry of Wilson loop diagrams

### 2019-02-25 General WLD combinatorics.tex
some comments on the comments in lemma 3.7

\begin{rmk}\label{rem:props of length 2 and 3} \sanote{change remark to "Configurations"?}
The following observations about propagators of short length in an (weakly) admissibly Wilson loop diagram, $W$, are easily verified:
\begin{enumerate}
\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
\item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.
\end{enumerate}
\end{rmk}

@@

\begin{lem}\label{lem sian}
  Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs.
  \begin{enumerate}
    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 inside it and nothing else inside it.\label{item big and 2} \sanote{doesn't this depend on which side you call inside? Should we say ``on one side''?}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
\end{lem}

\begin{proof} \sanote{fixed misuse of the word support in lemma}
Suppose first that $W$ has a propagator of length $3$, say $p=(i, i+3)$.  By Remark~\ref{rem:props of length 2 and 3} and the fact that every vertex of $W$ supports at least one propagator, we have that $i+2$ supports exactly one propagator and this propagator must have length 2 by noncrossingness.  This gives us an instance of configuration~\ref{item big and 2} from the statement.

Now suppose $W$ has no propagators of length $3$. \sanote{when do we deal with this restriction?}
%  We will prove the following stronger result: that $D$ admits a pair of propagators of length 2 in the following configuration:
%\begin{equation}\label{eq:2 prop config}
%\begin{tikzpicture}[baseline=(current bounding box.east)]
%\pgfmathsetmacro{\radius}{2}
%\pgfmathsetmacro{\angle}{20}
%
%\begin{scope}
%\clip (-\radius*1.1,\radius*0.25) rectangle (\radius*1.1,\radius*1.25);
%
%\begin{scope}
%\clip (-\radius*1.1,\radius*0.45) rectangle (\radius*1.1,\radius*1.1);
%\draw[-] (0,0) circle[radius=\radius cm];
%\end{scope}
%
%% vertices
%\foreach \i in {2,3,...,7}{
%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
%}
%
%\begin{scope}
%\clip (0,0) circle[radius=\radius];
%\draw[propagator] (2.5*\angle:\radius*1.1 cm) to [bend left=90] (4.35*\angle:\radius*1.1 cm);
%\draw[propagator] (4.65*\angle:\radius*1.1 cm) to [bend left=90] (6.5*\angle:\radius*1.1 cm);
%
%\end{scope}
%
%\node at (80:\radius*1.1) {\tiny $j$};
%\node at (100:\radius*1.1) {\tiny $j+1$};
%\node at (90:\radius*0.5) {\small $s_j = s_{j+1} = 2$};
%
%\end{scope}
%\end{tikzpicture}
%\end{equation}

@@

Now suppose $q_{r}$ exists by the induction hypothesis, oriented such that $(q_r, <_{i_r})$ and bounds a region $[i_r,k_r]$ on the outside. This region does not contain any $p_i$ for $i\leq r$. \sanote{Know what $p_1$ is. What are the others?}  Consider the restricted diagram $W_r:=W_{[i_r,k_r]}$; by the original hypotheses on $W$ every vertex $l \in [i_r+2,k_r-2]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $l \in \{i_r,i_r+1,k_r-1,k_r\}$ because these vertices support $q_r$.

>>>>

\begin{rmk}\label{rem:props of length 2 and 3} 
The following observations about configurations of propagators of short length in an (weakly) admissibly Wilson loop diagram, $W$, are easily verified:
\begin{enumerate}
\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
\item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.
\end{enumerate}
\end{rmk}

@@

\begin{lem}\label{lem sian}
  Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs.
  \begin{enumerate}
    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 inside it and nothing else inside it.\label{item big and 2} \sanote{doesn't this depend on which side you call inside? Should we say ``on one side''?  -- the point is that the inside should be the length 6 side.  Now there could be two length 6 sides in which case, yes there should exist one of the length 6 sides with the desired property.  I'm not sure how you want to phrase all this}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
\end{lem}

\begin{proof}
Suppose first that $W$ has a propagator of length $3$, say $p=(i, i+3)$.  By Remark~\ref{rem:props of length 2 and 3} and the fact that every vertex of $W$ supports at least one propagator, we have that $i+2$ supports exactly one propagator and this propagator must have length 2 by noncrossingness.  This gives us an instance of configuration~\ref{item big and 2} from the statement.

Now suppose $W$ has no propagators of length $3$.
%  We will prove the following stronger result: that $D$ admits a pair of propagators of length 2 in the following configuration:
%\begin{equation}\label{eq:2 prop config}
%\begin{tikzpicture}[baseline=(current bounding box.east)]
%\pgfmathsetmacro{\radius}{2}
%\pgfmathsetmacro{\angle}{20}
%
%\begin{scope}
%\clip (-\radius*1.1,\radius*0.25) rectangle (\radius*1.1,\radius*1.25);
%
%\begin{scope}
%\clip (-\radius*1.1,\radius*0.45) rectangle (\radius*1.1,\radius*1.1);
%\draw[-] (0,0) circle[radius=\radius cm];
%\end{scope}
%
%% vertices
%\foreach \i in {2,3,...,7}{
%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
%}
%
%\begin{scope}
%\clip (0,0) circle[radius=\radius];
%\draw[propagator] (2.5*\angle:\radius*1.1 cm) to [bend left=90] (4.35*\angle:\radius*1.1 cm);
%\draw[propagator] (4.65*\angle:\radius*1.1 cm) to [bend left=90] (6.5*\angle:\radius*1.1 cm);
%
%\end{scope}
%
%\node at (80:\radius*1.1) {\tiny $j$};
%\node at (100:\radius*1.1) {\tiny $j+1$};
%\node at (90:\radius*0.5) {\small $s_j = s_{j+1} = 2$};
%
%\end{scope}
%\end{tikzpicture}
%\end{equation}

@@

Now suppose $q_{r}$ exists by the induction hypothesis, oriented such that $(q_r, <_{i_r})$ and bounds a region $[i_r,k_r]$ on the outside. This region does not contain any $p_i$ for $i\leq r$. \sanote{Know what $p_1$ is. What are the others?, they are the things we are inductively constructing and so they are about to be defined inductively (see the next paragraph)}  Consider the restricted diagram $W_r:=W_{[i_r,k_r]}$; by the original hypotheses on $W$ every vertex $l \in [i_r+2,k_r-2]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $l \in \{i_r,i_r+1,k_r-1,k_r\}$ because these vertices support $q_r$.
